systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-12-10 paper/trunk/systemfit.tex
added appendix (table) to compare values returned by systemfit() and values returned by lm()
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@695 591db2bd-e0a0-4d22-8c19-2192dbb7da31
updated path to our department's BibTeX data base
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@708 591db2bd-e0a0-4d22-8c19-2192dbb7da31
substituted "\COV" (defined in jss.cls) for all "\Cov"; removed definition(s) of "\Cov"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@710 591db2bd-e0a0-4d22-8c19-2192dbb7da31
The paper no longer treats Omega as known in sections 2.1 an

\documentclass[article]{jss}
\usepackage[pdftex]{thumbpdf}
%   run: pdflatex *.tex -> thumbpdf *.tex -> pdflatex *.tex
\usepackage{csquotes}
\MakeOuterQuote{°}
\usepackage{amsmath}
\usepackage{float}

\usepackage{lineno}

\linenumbers

\newcommand{\Cov}{\text{Cov}}
\clubpenalty=10000
\widowpenalty=10000

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{systemfit} % a subset of my big bibtex file
%\bibliography{/home/suapm095/Documents/Literatur/arne}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[article]{jss}
\usepackage{csquotes}
\MakeOuterQuote{°}
\usepackage{amsmath}
\usepackage{float}

% \usepackage{lineno}
% 
% \linenumbers

\newcommand{\bHat}{\hat{\beta}}
\newcommand{\COVHat}{\widehat{\COV}}
\newcommand{\lHat}{\hat{\lambda}}
\newcommand{\OHat}{\widehat{\Omega}}
\newcommand{\SHat}{\widehat{\Sigma}}
\newcommand{\sHat}{\hat{\sigma}}
\newcommand{\uHat}{\hat{u}}
\newcommand{\XHat}{\widehat{X}}
\clubpenalty=10000
\widowpenalty=10000
\setlength{\emergencystretch}{3em}
% \setlength{\overfullrule}{5pt}

\newcommand{\codeD}[2]{\code{#1}\hspace{0pt}\code{.#2}}
\newcommand{\codeDD}[3]{\code{#1}\hspace{0pt}\code{.#2}\hspace{0pt}\code{.#3}}
\newcommand{\codeDDD}[4]{\code{#1}\hspace{0pt}\code{.#2}\hspace{0pt}%
\code{.#3}\hspace{0pt}\code{.#4}}

@@

\section*{Acknowledgments}
We thank Achim Zeileis, John Fox, Ott Toomet, William H.\ Greene,
two anonymous referees
and several users of \pkg{systemfit}
for their comments and suggestions
that helped us to improve the \pkg{systemfit} package as well as this paper.
Of course, any remaining errors are the authors'.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{systemfit} % a subset of my big bibtex file
%\bibliography{agrarpol}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\input{systemfit_compare_lm.tex}

\input{systemfit_timings.tex}

\input{systemfit_sem.tex}
